% Created 2024-02-20 Tue 14:20
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{placeins}
\usepackage{gensymb}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{tikz-uml}
\author{Christian Johnson\and\&\and Dan Nusraty\and\&\and Dylan Mcgill\and\newline Optimail}
\date{\today}
\title{Mail Database Project}
\hypersetup{
 pdfauthor={Christian Johnson\and\&\and Dan Nusraty\and\&\and Dylan Mcgill\and\newline Optimail},
 pdftitle={Mail Database Project},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2.50 (Org mode 9.7-pre)}, 
 pdflang={English}}
\begin{document}

\maketitle
\section*{Main Entities}
\label{sec:org488e9c5}
\begin{itemize}
\item User (Mailroom Employee)
\item Package
\item Database
\item Database Tables
\item Application/System
\item Email
\item Cadet
\end{itemize}
\section*{Attributes}
\label{sec:orgf977227}
\subsection*{User}
\label{sec:orgc0e556a}
\begin{itemize}
\item Username
\item Password
\item Access Priviledge
\end{itemize}
\subsection*{Package}
\label{sec:org02e8db0}
\begin{itemize}
\item Tracking Number
\item Addressee
\item Address
\end{itemize}
\subsection*{Database}
\label{sec:orgfea8380}
\begin{itemize}
\item Name
\item Filepath
\item Sqlite3 Connection
\item Sqlite3 Cursor
\item Tables
\end{itemize}
\subsection*{Table}
\label{sec:orgf77cee0}
\begin{itemize}
\item Properties
\item Name
\end{itemize}
\subsection*{Email}
\label{sec:orga1072e2}
\begin{itemize}
\item Addressee
\item Subject
\item Content
\end{itemize}
\subsection*{System}
\label{sec:orgc046103}
\begin{itemize}
\item GUI state
\end{itemize}
\subsection*{Cadet}
\label{sec:org9306f4c}
\begin{itemize}
\item Name
\item Email
\item Box Number
\item Graduation Date
\end{itemize}
\section*{Relationships}
\label{sec:org399f906}
A single database will contain several tables.
A single table will contain several Cadets.
A single table will contain several packages.
A single table will contain several users.
A single cadet can be associated with several packages.
A single cadet can receive several emails.
A single package can be associated with several emails.
A single application can be associated with several users.
A single application is associated with at least 3 database tables.
\section*{Constraints}
\label{sec:org4fc1174}
???
\section*{Domain Model}
\label{sec:org3f1ac46}


\section*{Class Diagram}
\label{sec:org6e8af8b}

\begin{tikzpicture}
  \umlclass[x=0,y=0]{User}{
    - Username : string \\
    - Password : string \\
    - AccessPrivilege : string
  }{}

  \umlclass[x=0,y=-3]{Package}{
    - TrackingNumber : string \\
    - Addressee : string \\
    - Address : string
  }{}

  \umlclass[x=0,y=-6]{Database}{
    - Name : string \\
    - Filepath : string \\
    - SQLite3Connection \\
    - SQLite3Cursor \\
    - Tables : Table[]
  }{}

  \umlclass[x=0,y=-9]{Table}{
    - Properties : string \\
    - Name : string \\
    - Cadets : Cadet[]
    - Packages : Package[]
    - Users : User[]
  }{}

  \umlclass[x=0,y=-12]{Email}{
    - Addressee : string \\
    - Subject : string \\
    - Content : string
  }{}

  \umlclass[x=0,y=-15]{System}{
    - GUIState : string \\
    - Users : User[]
    - Databases : Database[]
    - Tables : Table[]
  }{}

  \umlclass[x=0,y=-18]{Cadet}{
    - Name : string \\
    - Email : string \\
    - BoxNumber : string \\
    - GraduationDate : date \\
    - Packages : Package[]
    - Emails : Email[]
  }{}

  %\umlassoc[mult1=*, pos1=0.1, mult2=1, pos2=0.9]{Database}{Table}
  %\umlassoc[mult1=*, pos1=0.1, mult2=*, pos2=0.9]{Table}{Cadet}
  %\umlassoc[mult1=*, pos1=0.1, mult2=*, pos2=0.9]{Table}{Package}
  %\umlassoc[mult1=*, pos1=0.1, mult2=*, pos2=0.9]{Table}{User}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{Cadet}{Package}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{Cadet}{Email}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{Package}{Email}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{System}{User}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{System}{Database}
  %\umlassoc[mult1=1, pos1=0.1, mult2=*, pos2=0.9]{System}{Table}
\end{tikzpicture}
\end{document}